---
title: "hw-5"
author: "Hector He"
date: "5/15/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pokemon <- read.csv('~/Desktop/Spring 2022/PSTAT 131/homework/homework-5/data/Pokemon.csv')
library(tidymodels)
library(tidyverse)
library(readr)
library(dplyr)
head(pokemon, n = 8)
```

Exercise 1
Install and load the janitor package. Use its clean_names() function on the Pokémon data, and save the results to work with for the rest of the assignment. What happened to the data? Why do you think clean_names() is useful?
```{r}
library(janitor)
pokemon <- clean_names(pokemon)
head(pokemon)
```
column names are changed, now only including lower case letters and "_" symbols, which are easier to access


Exercise 2
Using the entire data set, create a bar chart of the outcome variable, type_1.
How many classes of the outcome are there? Are there any Pokémon types with very few Pokémon? If so, which ones?
```{r}
#ggplot(data = pokemon, aes(x = type_1)) + geom_bar()
ggplot(data = pokemon, aes(x = reorder(factor(type_1), type_1, function(x)-length(x)))) + geom_bar() + labs(x = 'type_1')
```
Type 1 Poison, Fighting, Steel, Ice, Fairy, Flying have less than 30 counts, especially Type 1 Flying has less than 10 counts

```{r}
pokemon <- filter(pokemon, type_1=='Bug'|type_1=='Fire'|type_1=='Grass'|type_1=='Normal'|type_1=='Water'|type_1=='Psychic')
head(pokemon, n = 15)
```
```{r}
pokemon <- pokemon %>%
  mutate(type_1 = factor(type_1)) %>%
  mutate(legendary = factor(legendary))
tail(pokemon, n=10)
```


Exercise 3
Perform an initial split of the data. Stratify by the outcome variable. You can choose a proportion to use. Verify that your training and test sets have the desired number of observations.
Next, use v-fold cross-validation on the training set. Use 5 folds. 
```{r}
set.seed(2000)
pokemon_split <- initial_split(pokemon, prop = 0.75, strata = type_1)
pokemon_test <- testing(pokemon_split)
pokemon_train <- training(pokemon_split)
```

```{r}
dim(pokemon_train)
dim(pokemon_test)
```
```{r}
pokemon_folds <- vfold_cv(pokemon_train, v = 5, strata = type_1)
pokemon_folds
```


Exercise 4
Set up a recipe to predict type_1 with legendary, generation, sp_atk, attack, speed, defense, hp, and sp_def.
```{r}
pokemon_recipe <- recipe(type_1 ~ legendary+generation+sp_atk+attack+speed+defense+hp+sp_def, data = pokemon_train) %>% 
  step_dummy(c(legendary, generation)) %>%
  step_center(all_predictors()) %>% 
  step_scale(all_predictors()) 
```


Exercise 5
```{r}
library(glmnet)
pokemon_tuned <- 
  multinom_reg(penalty = tune(), mixture = tune()) %>% 
  set_mode("classification") %>% 
  set_engine("glmnet")
```

```{r}
pokemon_wkflow_tuning <- workflow() %>% 
  add_recipe(pokemon_recipe) %>% 
  add_model(pokemon_tuned)
```


Exercise 6
```{r}
pokemon_grid <- grid_regular(penalty(range = c(-5, 5)), mixture(range = c(0, 1)), levels = 10)
pokemon_grid
```
There will be 10*10 = 100 models fitted into the folded data


Exercise 7
```{r}
pokemon_tune_res <- tune_grid(pokemon_wkflow_tuning, resamples = pokemon_folds, grid = pokemon_grid)
pokemon_tune_res
```

```{r}
autoplot(pokemon_tune_res)
```
```{r}
collect_metrics(pokemon_tune_res)
```
```{r}
pokemon_best_tuned <- select_best(pokemon_tune_res, metric = "roc_auc")
pokemon_best_tuned
```
```{r}
pokemon_final <- finalize_workflow(pokemon_wkflow_tuning, pokemon_best_tuned)
pokemon_final_fit <- fit(pokemon_final, data = pokemon_train)
```


Exercise 8
```{r}
augment(pokemon_final_fit, new_data = pokemon_test) %>% 
  roc_auc(type_1, .pred_Bug:.pred_Water)
```
```{r}
augment(pokemon_final_fit, new_data = pokemon_test) %>%
  roc_curve(truth = type_1, estimate = .pred_Bug:.pred_Water) %>%
  autoplot()
```
works the best on type "Grass"






